Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex

Optionally, our algorithm can be initialized using proposal bounding boxes from state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before executing the two steps above. In this scenario, our approach provides a means to augment standard bounding box detectors with more interesting 3D information.

\begin{comment}
Our method is in line with \cite{Aubry14, Lim14} in the sense that we
use only renderings, not real images. However, rather than using fixed
sized mid-level patches, we use whole objects and make root
templates. By using root templates, there is no need to learn a
discriminative patch dictionary or to calibrate the patches and an
additional inference stage is not required. However, whitening the
whole template is prohibitive for several reasons. All templates have
different aspect ratios making it difficult to generate the covariance
matrix $\Sigma$. Since the root templates are larger than mid-level
patches, a very large auto-covariance $\Gamma$ is required. Lastly,
time complexity of decorrelating a template with $n$ cells increases
as $O(n^3)$, resulting in slow template generation and large residuals
due to numerical errors accumulated while decomposing the covariance
matrix $\Sigma$.

@@

Table \ref{tab:who_initializations} provides a detailed comparison of WHO and NZ-WHO templates, illustrating that our method is faster and more discriminative than Whitened Histograms of Orientations. \scream{Does the table show this?}

\subsubsection{Generating $\Sigma$ and $\mu$}
\scream{this section seems important to understand the following section but it's also just a re-writing of the Hariharan method}
In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
generated from natural images. That is, they assume the mean of a HOG cell is
independent of its place in the image, and the autocovariance of cells depends
only on their relative location.

@@

We use the GPU to parallelize the lookup of the correct autocovariance cells
during covariance matrix syntheses, which is \scream{x} times faster than using
the CPU (Figure \ref{fig:covariancetime}).

@@

Our method begins by convolving the

>>>>

Our ensemble of NZ-WHO templates can work as a detector but our algorithm 
can be initialized using proposal bounding boxes from
state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before
executing the two steps above. In this scenario, our approach provides a means
to augment standard bounding box detectors with more interesting 3D
information.
\begin{comment}
Our method is in line with \cite{Aubry14, Lim14} in the sense that we
use only renderings, not real images. However, rather than using fixed
sized mid-level patches, we use whole objects and make root
templates. By using root templates, there is no need to learn a
discriminative patch dictionary or to calibrate the patches and an
additional inference stage is not required. However, whitening the
whole template is prohibitive for several reasons. All templates have
different aspect ratios making it difficult to generate the covariance
matrix $\Sigma$. Since the root templates are larger than mid-level
patches, a very large auto-covariance $\Gamma$ is required. Lastly,
time complexity of decorrelating a template with $n$ cells increases
as $O(n^3)$, resulting in slow template generation and large residuals
due to numerical errors accumulated while decomposing the covariance
matrix $\Sigma$.

@@

In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
generated from natural images. That is, they assume the mean of a HOG cell is
independent of its place in the image, and the autocovariance of cells depends
only on their relative location.

@@

We use the GPU to parallelize the lookup of the correct autocovariance cells
during covariance matrix syntheses. The real time analysis for various number of cells is on Figure \ref{fig:covariancetime}).

@@
